Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-11-02 doc/manuscript/manuscript.Rmd
add link to SOM to address #15

The analysis of molecular variance (AMOVA) for clone-corrected samples over the hierarchy of Region, Source, and Year showed significant variation between Regions and Years, but no significant variation between wmn and producer fields (Table \@ref(tab:amova)).
In contrast, when we compared the three cultivars, Beryl, Bunsi, and G122, we found no significant differentiation (Supplementary Information).

>>>>

The analysis of molecular variance (AMOVA) for clone-corrected samples over the hierarchy of Region, Source, and Year showed significant variation between Regions and Years, but no significant variation between wmn and producer fields (Table \@ref(tab:amova)).
In contrast, when we compared the three cultivars, Beryl, Bunsi, and G122, we found no significant differentiation (Supplementary Information[^1]).

[^1]: https://github.com/everhartlab/sclerotinia-366/blob/v1.0/results/wmn-differentiation.md#host-differentiation
